Version 0.1 dated 10 March 2025
\begin{itemize}
    \item First draft with a description of the main analysis features.
\end{itemize}


Version 0.2 dated 26 March 2025
\begin{itemize}
    \item Second draft with updates following extensive feedback from QBH expert D. Gingrich and LpX Conveners.
    \item Clarifications/corrections in numerous sections.
    \item Updates in analysis strategy (blinding strategy addition).
    \item Added text regarding discovery statistics in results chapter.
    \item Updates systematics ratio plots
    \item Corrected CR/VR plots (post-fit corrects bkg. modelling per data)
    \item Added SR plots and binning description
    \item Updates regarding \texttt{mc23e} derivation production status
\end{itemize}


Version 0.3 dated 3 October 2025
\begin{itemize}
    \item Third draft with updates following extensive feedback from EB.
    \item Inclusion of \texttt{data24} and \texttt{mc23e}.
    \item Small changes to region definitions.
    \item Updates to fakes:
    \begin{itemize}
        \item Inclusion of 2024, re-estimation and validation.
        \item Derivation of systematic uncertainties.
    \end{itemize}
    \item Updated systematics ratio plots:
    \begin{itemize}
        \item Including \texttt{mc23e}, updated plots and confirmation from CP groups.
        \item Solution to known MCP issue.
    \end{itemize}
    \item Updated limit plots, including 2024.
\end{itemize}


Version 0.4 dated 3 November 2025
\begin{itemize}
    \item Removing small notes about future inclusion of 2024 data.
    \item Object definition chapter to include clearer description of recommendations used per each data-taking year and corresponding MC campaign.
    \item Fakes
    \begin{itemize}
        \item Textual updates.
        \item Fake with up/down stat/syst in SR plot added.
        \item Clarifications in Object Definition chapter, including about recommendations used per-year per-campaign.
        \item Updated fit results on a par with
        \begin{itemize}
            \item Proper handling of \texttt{Sherpa} PDF set (one NP)
            \item \texttt{DropNorm} for \texttt{Sherpa} PDF uncertainties in SR
            \item Finer SR binning (optimised)
        \end{itemize}
        \item Added multi-binned $W$ CRVR fit following EB's requests to confirm no shape effects.
        \item Corrected issues commented by LpX Conveners.
        \item Finalised resolution-informed binning study in Results and Appendix.
    \end{itemize} % <-- CLOSING THE MAIN V0.4 ITEMIZE
\end{itemize}


Version 0.5 dated 28 November 2025
\begin{itemize}
    \item Small update in limit plotting.
    \item Adding limits for ADDn4 and ADDn2 models
    \item Fixing small typo in changelog
    \item Fixing several wrong/outdated statements in Results
    \item Fixing several wrong/outdated statements in Conclusions
    \item Fix typo in appendix section name
    \item Fixing based on post-unblinding CDS comments: fakes, bkg. modelling, systematic uncertainties and more.
    \item Adding SR plots with updated binning scheme.
    \item Adding appendix discussion of comparison to Run1 and Run2 QBH results.
    \item Many updated on a par with post-unblinding request CDS comments by:
    \begin{itemize}
        \item LpX Conveners
        \item EB
        \item CP liaisons
        \item Experts reviewers
    \end{itemize}
\end{itemize}


Version 0.6 dated 10 December 2025
\begin{itemize}
    \item Added PRW uncertainty (and mentioned in systematics chapter).
    \item Added luminosity uncertainty mention in systematics chapter.
    \item Removed \texttt{DropNorm} configuration from fit.
    \item Scaled PDF variations to the nominal across all regions; now considered as shape-only.
    \item Separated theory nuisance parameters per process, $W$+jets and $Z$+jets; alleviated large $\mu_W$ and $\mu_Z$ correlations.
    \item Added $\chi^{2}$-inclusive multibinned $W$+jets CRVR fit plots.
    \item Updated Appendix w/ clearer discussion of $\mathcal{A}\times\epsilon$, with comparisons to Run1 and Run2 QBH results.    
\end{itemize}