Following the \href{https://twiki.cern.ch/twiki/bin/viewauth/Atlas/DataPreparationCheckListForPhysicsAnalysis}{recommendations} of the DataPrep group, the following event-level requirements are made. We use the official GRLs to ensure a fully working detector during data taking:
\begin{itemize}
    \item \scriptsize \texttt{data22\_13p6TeV.periodAllYear\_DetStatus-v109-pro28-04\_MERGED\_PHYS\_StandardGRL\_All\_Good\_25ns\_ignore\_TRIGLAR.xml}
    \item \scriptsize \texttt{data23\_13p6TeV.periodAllYear\_DetStatus-v110-pro31-06\_MERGED\_PHYS\_StandardGRL\_All\_Good\_25ns.xml}
    \item \scriptsize \textcolor{red}{\texttt{physics\_25ns\_data24.xml}}
\end{itemize}

There is some ambiguity for the Run3 datasets which GRLs\footnote{\href{https://twiki.cern.ch/twiki/bin/viewauth/AtlasProtected/GoodRunListsForAnalysisRun3\#\#GRL\_for\_2024\_pp\_collision\_data\_l}{https://twiki.cern.ch/twiki/bin/viewauth/AtlasProtected/GoodRunListsForAnalysisRun3\#\#GRL\_for\_2024\_pp\_collision\_data\_l}} to use. We chose the GRL which is applicable
for the whole analysis. For 2022 our choice represents the GRL that is suitable for analyses relying with muon triggers (as these are used in the muon+jet channels) while for 2023 it represents the GRL suitable for jet triggers (as these are used in the fake-lepton estimation). 
The following event-level vetoes are made to reject bad/corrupt events:

\begin{itemize}
    \item LAr noise burst and data corruption (\texttt{xAOD::EventInfo::LAr});
    \item Tile corrupted events (\texttt{xAOD::EventInfo::Tile});
    \item events affected by the SCT recovery procedure for single event upsets (\texttt{xAOD::EventInfo::SCT});
    \item incomplete events (\texttt{xAOD::EventInfo::Core}).
\end{itemize}

Debug stream events have not been included. 
Events are required to have a primary vertex with at least two associated tracks. The primary vertex is
selected as the one with the largest $\Sigma p^{2}_{\textrm{T}}$, where the sum is over all tracks with transverse momentum
$p_{\textrm{T}} > 0.4~\textrm{GeV}$ that are associated with the vertex.

Furthermore, events in which a jet does not pass the \textit{Loose} jet cleaning criteria\footnote{\href{https://cds.cern.ch/record/2037702/files/ATLAS-CONF-2015-029.pdf}{https://cds.cern.ch/record/2037702/files/ATLAS-CONF-2015-029.pdf}} are vetoed to reject
non-collision backgrounds and jets from calorimeter noise. This strictly follows the recommendations\footnote{\href{https://twiki.cern.ch/twiki/bin/view/AtlasProtected/HowToCleanJetsR21}{https://twiki.cern.ch/twiki/bin/view/AtlasProtected/HowToCleanJetsR21}} from the JetEtmiss CP group, so we don’t specify the detailed jet-cleaning requirements here.